\thetitle

### 2017-12-05 TeX/manuscript.tex
added to background and methods of manuscript

\begin{abstract}
    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does. A fundamental difference between human neural network and current machine neural networks is that only human networks combine symbolic reasoning with computation. Here we show how a graph can \ldots
\end{abstract}
\newpage

@@

@@

While this model is suitable for biological networks of neurons, a neural network in the computational sense would look more like an abstract syntax tree. In the following diagram, a network of operators and operands form a tree-like structure in which elements at lower levels represent values to manipulate which at higher levels interact with each other through arithmetic operations to produce a result. Any computation which involves a combination of operations on one or more values can be represented in this structure, such as logical operations or large-scale machine learning models.

@@

\comment{
 \begin{figure}
 \centering
 \begin{tikzpicture}

@@

 \end{tikzpicture}
 \caption{An Abstract Syntax Tree of logical operations. \label{fig:sig-neuron}} 
\end{figure}
}

\textcolor{red}{
Research Idea: In a neural network, rather than just weights being updated through training algorithms, the operations by which the outputs to weights are combined is trained as well. In other words, instead of the inputs to each neuron being added together then put through an activation function, they may be multiplied, subtracted, divided, etc }

>>>>

\begin{abstract}
    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does. A fundamental difference between human neural network and current machine neural networks is that only human networks combine symbolic reasoning with computation.
\end{abstract}
\newpage

@@

	Neural networks have been used for decades to solve a wide variety of machine learning tasks without the need for explicit programming of the solutions to be done by humans. Typically the networks only make use of arithmetic computation, meaning that logical operations are not incorportated into the models. This hasn't been done because there is no clear method by which logical information (TRUE/FALSE) should be converted to numerical information, and vice versa. In Computer Science, True and False are generally represented as 1 and 0, respectively, whereas in Mathematics, they are often represented as -1 and 1 \textcolor{red}{Which specific fields of Math and Compsci?}. Our research aims to construct a neural network which effectively combines logical and arithmetic computation, and apply this network to a problem which demostrates it's ability to perform symbolic reasoning.

@@

While this model is suitable for biological networks of neurons, a neural network in the computational sense would look more like an abstract syntax tree. In the following diagram, a network of operators and operands form a tree-like structure in which elements at lower levels represent values to manipulate which at higher levels interact with each other through arithmetic operations to produce a result. Any computation which involves a combination of operations on one or more values can be represented in this structure, such as logical or arithmetic operations.

@@

@@

 \end{tikzpicture}
 \caption{An Abstract Syntax Tree of logical operations. \label{fig:sig-neuron}} 
\end{figure}
